% !TEX root = ./resume.tex

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot[C]{\thepage} % Add page numbers at the center of the footer
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\setlength{\footskip}{13.59999pt}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated PDF is machine-readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeEducationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small#4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%

\begin{document}

%---------- HEADING ----------

\begin{center}
  \textbf{\Huge Muhammad Zeeshan Ahmad} \\ \vspace{3pt}
  \small
  \faMobile \hspace{.5pt} \href{tel:923004761002}{+92 300 476 1002}
  $|$
  \faAt \hspace{.5pt} \href{mailto:itexpert120@outlook.com}{itexpert120@outlook.com}
  $|$
  \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/itexpert120}{LinkedIn}
  $|$
  \faGithub \hspace{.5pt} \href{https://github.com/itexpert120}{GitHub}
  $|$
  \faMapMarker \hspace{.5pt} {Multan, Pakistan}
\end{center}


%----------- EDUCATION -----------

\section{Education}
\vspace{3pt}
\resumeSubHeadingListStart

\resumeEducationHeading
{The Islamia University of Bahawalpur}{Bahawalpur, Pakistan}
{Bachelor of Science in Computer Systems Engineering; \textbf{CGPA: 3.71/4.00}}{Sep 2021 \textbf{--} Present}

\resumeSubHeadingListEnd

%----------- SKILLS -----------

\section{Skills}
\vspace{2pt}
\resumeSubHeadingListStart
\small{\item{
    \textbf{Core:} TypeScript, JavaScript (ES6+), HTML5, CSS3 \\ \vspace{3pt}
    \textbf{Frontend:} React.js, Next.js, TanStack Query, Zustand, Tailwind CSS, Chakra UI, Framer Motion, shadcn/ui \\ \vspace{3pt}
    \textbf{Testing \& Tools:} Jest, React Testing Library, Playwright, Git, GitHub Actions, Vite, npm/yarn/pnpm/bun \\ \vspace{3pt}
    \textbf{API Integration:} RESTful APIs, GraphQL, OpenAPI/Swagger \\ \vspace{3pt}
    \textbf{Cloud \& Deployment:} Vercel, Netlify, Docker \\ \vspace{3pt}
    \textbf{Methodologies:} Component-Driven Development, Responsive Design, Mobile-First Approach,  CI/CD
}}
\resumeSubHeadingListEnd

%----------- EXPERIENCE -----------

\section{Experience}
\vspace{3pt}
\resumeSubHeadingListStart

\resumeSubheading
{NEARBuilders}{Remote Part Time}
{Frontend Engineer}{Sep 2023 \textbf{--} Present}
\resumeItemListStart
\resumeItem{\textbf{BetVex} $|$ \emph{\href{https://betvex.xyz}{\color{blue}Website}}
  \resumeItemListStart
  \resumeItem{
    Led a comprehensive UI overhaul of the dashboard, implementing modern design principles and enhancing user experience with responsive layouts and intuitive navigation.}
  \resumeItem{
    Integrated GraphQL indexer for real-time data fetching, optimizing performance and reducing load times by 40\% while ensuring seamless data synchronization.}
  \resumeItem{
    Executed a major UI uplift by implementing component-based architecture, improving code maintainability and establishing a consistent design system across the platform.}
  \resumeItemListEnd
}
\resumeItem{
  \vspace{9pt}
  \textbf{NEAR Catalog} $|$ \emph{\href{https://nearcatalog.xyz}{\color{blue}Website}}
  \resumeItemListStart
  \resumeItem{
    Architected and developed a full-featured catalog platform using Next.js, TypeScript, and React Query, showcasing NEAR blockchain projects with optimized SEO and performance.}
  \resumeItem{
    Implemented dynamic data fetching and caching strategies using React Query, reducing API calls by 60\% while maintaining real-time project updates.}
  \resumeItem{
    Engineered a responsive and type-safe UI with TypeScript and modern React patterns, achieving a 90+ Lighthouse score for performance and accessibility.}
  \resumeItemListEnd
}
\resumeItem{
  \vspace{9pt}
  \textbf{Redacted Event App}
  \resumeItemListStart
  \resumeItem{
    Engineered a modular event platform using React, Vite, and TypeScript, with a reusable architecture that allows rapid deployment for different events while requiring minimal code changes.}
  \resumeItem{
    Implemented core features including QR code authentication, wallet integration, and user-to-user transactions using React Query for efficient state management and real-time updates.}
  \resumeItem{
    Developed a scalable component system with Chakra UI, encompassing profile management, event navigation, and interactive reward systems, resulting in 70\% code reusability across different events.}
  \resumeItemListEnd
}
\resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeSubheading
{Upwork}{Remote Freelance}
{Frontend Engineer}{Aug 2024 \textbf{--} Present}
\resumeItemListStart
\resumeItem{\textbf{GetCULTD} $|$ \emph{\href{https://app.getcultd.com}{\color{blue}Website}}
 \resumeItemListStart
 \resumeItem{
   Architected and developed a comprehensive CRM dashboard using Next.js, integrating shadcn-ui and TailwindCSS to create a polished, professional interface for KOL management.}
 \resumeItem{
   Implemented advanced features including secure authentication, dynamic search functionality, and a Kanban board system, enabling efficient influencer campaign management and tracking.}
 \resumeItem{
   Built a multi-platform solution comprising both an admin dashboard and a public campaign website, facilitating seamless interaction between KOLs and campaign managers with React Query for real-time data synchronization.}
 \resumeItemListEnd
}
\resumeItemListEnd
\resumeSubHeadingListEnd

%----------- AWARDS & ACHIEVEMENTS -----------

\section{Awards \& Achievements}
\vspace{2pt}
\resumeSubHeadingListStart
\small{\item{
   \textbf{ETHDenver 2023 BUIDLathon Runner-up:} Secured 2nd place among 200+ teams by developing a decentralized events platform leveraging NEAR Protocol's social contracts. The solution enabled secure event management and social interactions in Web3 space. \\ \vspace{3pt}
}}
\resumeSubHeadingListEnd

\end{document}
